### 2015-03-02 fundamentals/impl.tex
addresses the concern by Erich: ' exclusive of what?  this isn't clear'

Any potential resource transfer, i.e., a bid or a request, may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.  In combination with the notion of mutual requests, complex instances
of supply and demand are enabled.

@@

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

>>>>

Any potential resource transfer, i.e., a bid or a request, may be denoted as
\textit{exclusive}. An exclusive transfer excludes partial fulfilment; it must
either be met fully or not at all. This mode supports concepts such as the
trading of individual reactor assemblies.  In combination with the notion of
mutual requests, complex instances
of supply and demand are enabled.

@@

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, \glspl{LP} solve much faster than
\glspl{MILP}. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.
